Using traffic analysis to identify The Second Generation Onion Router

### 2011-02-26 thesis/thesis.tex
Research methodology

Anonymous networks provide security for users by obfuscating messages with
encryption and hiding communications amongst cover traffic provided by other
network participants. In the academic literature, traditionally these networks
have been attacked with techniques that aim to uncover the identify of
participants. But the success of an anonymous network relies not only on it's
technical capabilities, but on adoption by a large enough user base to provide
adequate cover traffic. If anonymous network participants can be identified, the
users can be harassed, discouraging participation. Tor is an example of widely
used anonymous network which uses a form of Onion Routing to provide low latency
anonymous communications. This paper demonstrates that traffic from a simulated
Tor network can be distinguished from regular encrypted traffic, suggesting that
real world Tor users may be vulnerable to the same analysis.

@@

The proposed research will use a methodology typical of machine learning
traffic analysis papers, substituting data captured from a controlled
simulation in place of live network captures.

The experiment will be conducted in two phases, the first being a data
collection phase. The second phase will include a quasi experimental
methodology which will include data manipulation techniques to prepare the
collected data and a comparison of various heuristics and machine learning
based traffic analysis to classify the collected data.

>>>>

Anonymous networks provide security for users by obfuscating messages with
encryption and hiding communications amongst cover traffic provided by other
network participants. The traditional goal of academic research into these
networks has been attacks that aim to uncover the identity of network users.
But the success of an anonymous network relies not only on it's technical
capabilities, but on adoption by a large enough user base to provide adequate
cover traffic. If anonymous network nodes can be identified, the users
can be harassed, discouraging participation. Tor is an example of widely used
anonymous network which uses a form of Onion Routing to provide low latency
anonymous communications. This paper demonstrates that traffic from a simulated
Tor network can be distinguished from regular encrypted traffic, suggesting that
real world Tor users may be vulnerable to the same analysis.

@@

\section{Research Methodology}

The experiment conducted in this paper utilize a non-equivalent group design.
The experimental groups are generated using simulations which allow for a great
deal of control over independent variables, ensuring minimal difference between
the control and treatment groups. Both experiment groups perform the exact same
simulations. The control group performs all simulations using regular HTTPS,
while the treatment group proxies all communications over Tor. The treatment
group can be broken into HTTP over Tor and HTTPS over Tor based simulations.
